diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2019-11-15 jss-article-rnw-diffEnrich/article.Rnw
testing appveyor build
added keywords and address to article.Rnw

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{JSS, style guide, comma-separated, not capitalized, \proglang{R}}
\Plainkeywords{JSS, style guide, comma-separated, not capitalized, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Achim Zeileis\\
  Journal of Statistical Software\\
  \emph{and}\\
  Department of Statistics\\
  Faculty of Economics and Statistics\\
  Universit\"at Innsbruck\\
  Universit\"atsstr.~15\\
  6020 Innsbruck, Austria\\
  E-mail: \email{Achim.Zeileis@R-project.org}\\
  URL: \url{https://eeecon.uibk.ac.at/~zeileis/}
}

>>>>

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{differential enrichment, KEGG REST API, \proglang{R}}
\Plainkeywords{differential enrichment, KEGG REST API, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Laura Saba\\
  University of Colorado\\
  Skaggs School of Pharmacy and Pharmaceutical Sciences\\
  Mail Stop C238\\
  12850 E. Montview Blvd. V20-2124\\
  Aurora, CO 80045\\
  E-mail: \email{Laura.Saba@cuanschutz.edu}\\
}

### 2019-11-15 jss-article-rnw-diffEnrich/article.tex
added keywords and address to article.Rnw

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{JSS, style guide, comma-separated, not capitalized, \proglang{R}}
\Plainkeywords{JSS, style guide, comma-separated, not capitalized, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Achim Zeileis\\
  Journal of Statistical Software\\
  \emph{and}\\
  Department of Statistics\\
  Faculty of Economics and Statistics\\
  Universit\"at Innsbruck\\
  Universit\"atsstr.~15\\
  6020 Innsbruck, Austria\\
  E-mail: \email{Achim.Zeileis@R-project.org}\\
  URL: \url{https://eeecon.uibk.ac.at/~zeileis/}
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

>>>>

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{differential enrichment, KEGG REST API, \proglang{R}}
\Plainkeywords{differential enrichment, KEGG REST API, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Laura Saba\\
  University of Colorado\\
  Skaggs School of Pharmacy and Pharmaceutical Sciences\\
  Mail Stop C238\\
  12850 E. Montview Blvd. V20-2124\\
  Aurora, CO 80045\\
  E-mail: \email{Laura.Saba@cuanschutz.edu}\\
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
